--- 
title: "Pokemon: A Brief Introduction to Starters"
author: "Benjamin Meek"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "Welcome to the wonderful world of Pokemon! This book is simply a practice book for a newcomer to RStudio, GitHub and bookdown. I apologize in advance for any mistakes in formatting, citation, or proper attributing to the Pokemon Co. and Nintendo. Enjoy!"
---
--- 
title: "Pokemon: A Brief Introduction to Starters"
author: "Benjamin Meek"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "Welcome to the wonderful world of Pokemon! This book is simply a practice book for a newcomer to RStudio, GitHub and bookdown. I apologize in advance for any mistakes in formatting, citation, or proper attributing to the Pokemon Co. and Nintendo. Enjoy!"
---

# Introduction {#intro}

Since this is a book about **Pokemon**, some of the tools I need to practice using are a little hard to include, like *math equations*. Currently there are $8*3+4=28$ starter Pokemon. There are 8 generations, with three starter Pokemon in each gen, for a total of 24, as well as a single starter for the *Let's Go Pikachu* and *Let's Go Eevee* games and Espeon and Umbreon in *Pokemon Colosseum*. 

For more information on any of the Pokemon discussed in this book, a great resource is the fan wiki, [Bulbapedia](https://bulbapedia.bulbagarden.net/wiki/Starter_Pok%C3%A9mon). The [Nintendo](https://www.nintendo.com/) website also includes regular updates on new games in the Pokemon franchise, which would mean the addition of more starters! For more about the basics, see Chapter \@ref(basics).

<!--chapter:end:index.Rmd-->

# The Basics {#basics}

This is going to be a short book that introduces the reader to the wonderful world of **Pokemon** and the starters in each game.

In every Pokemon game, the player starts with one of three Pokemon, usually a grass, water, or fire type. This first Pokemon is called the **starter**.

Each starter has 6 different base stats, meaning each has strengths and weaknesses. Here are some tables that show the base stats of each Gen 1 starter: Bulbasaur, Charmander, and Squirtle.

The first graph is **hit points** or **HP**, which is how much damage the Pokemon can take.

```{r nice-fig1, fig.cap='HP values for Gen 1 Starters', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(hitpoints)
```

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

```{r nice-tab2, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too.Or, if you don't know what you're doing, ask Dr. Macfarlane for help. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].

<!--chapter:end:01-intro.Rmd-->

# Literature

Here is a review of existing methods.

<!--chapter:end:02-literature.Rmd-->

# Methods

We describe our methods in this chapter.

<!--chapter:end:03-method.Rmd-->

# Applications

Some _significant_ applications are demonstrated in this chapter.

## Example one

## Example two

<!--chapter:end:04-application.Rmd-->

# Final Words

We have finished a nice book.

<!--chapter:end:05-summary.Rmd-->

`r if (knitr::is_html_output()) '
# References {-}
'`

<!--chapter:end:06-references.Rmd-->

